Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex

\extraspacing {\underline{\em Example 4.6.}} It is clear from Figure~\ref{fig:hv:type1:ex}d that $\cross_H(\alpha^*)$ contains $h_2, h_4$, and $h_5$, sorted in ascending order of y-coordinate. Recall that 
$\gbot(\bm{t}_1) = \gbot(\bm{t}_2) = \alpha'$. Both $\dcross_H(\bm{t}_1) = \set{h_2}$ and $\dcross_H(\bm{t}_2) = \set{h_2, h_4, h_5}$ are prefixes of the sorted list, as is consistent with Lemma~\ref{lmm:hv:type1:cross-r*}.
\done

>>>>

\extraspacing {\underline{\em Example 4.6.}} It is clear from Figure~\ref{fig:hv:type1:ex}d that $\cross_H(\alpha^*)$ contains $h_2, h_4$, and $h_5$, sorted in ascending order of their y-coordinates. Recall that $\gbot(\bm{t}_1) = \gbot(\bm{t}_2) = \alpha'$. Both $\dcross_H(\bm{t}_1) = \set{h_2}$ and $\dcross_H(\bm{t}_2) = \set{h_2, h_4, h_5}$ are indeed prefixes of the sorted $\cross_H(\alpha^*)$, as stated in Lemma~\ref{lmm:hv:type1:cross-r*}.
\done
